---
title: "P8130_HW2_wl2829"
author: "Wentong"
date: "10/6/2021"
output: pdf_document
---

# Problem 1
## Problem 1 (a)(b)
```{r echo = TRUE}
## problem 1 (a)
dbinom(24, size = 40, prob = 0.65)

## problem 1 (b)
pbinom(23, size = 40, prob = 0.65, lower.tail = FALSE)
```
## problem 1 (c)
### p = 0.65, q = 1 - 0.65 = 0.35, np > 5 and nq > 5, so we can use normal approximation to calcualte the probabilities. By using the continuity correction factor, we can use P(n-0.5<X<n+0.5) to replace P(X=n), P(X>n-0.5) to replace P(X>=n).
```{r}
### problem 1 (a)
pbinom(23.5, size = 40, prob = 0.65, lower.tail = FALSE)-pbinom(24.5, size = 40, prob = 0.65, lower.tail = FALSE)
### problem 1 (b)
pbinom(23.5, size = 40, prob = 0.65, lower.tail = FALSE)
```
### The approximation answer is equal to the original probabilities.


## Problem 1 (d)
### The expectation E is equal to
```{r echo = TRUE}
Expectation = np = 40 * 0.65
Expectation
```
## Problem 1 (e)
```{r}
sigma_sq = sqrt(40 * 0.65 * 0.35)
sigma_sq
```
### The SD is `r sigma_sq`.


# Problem 2
## Problem 2 (a)
```{r}
Lessthan3 = ppois(2, 7, lower.tail = TRUE) # the probability of having fewer than 3 tornados
Lessthan3
```

## Problem 2 (b)
```{r}
equalto3 = dpois(3, 7, log = FALSE) # the probability of having exactly 3 tornados
equalto3
```

## Problem 2 (c)
```{r}
morethan3 = ppois(3, 7, lower.tail = FALSE) # the probability of having more than 3 tornados
morethan3
```

# Problem 3
## Problem 3 (a)
```{r}
above137 = pnorm(137, mean = 132, sd = 9.8, lower.tail = FALSE)
above137
```
## Problem 3 (b)
```{r}
lessthan129 = pnorm(129, mean = 132, sd = 9.8, lower.tail = TRUE)
lessthan129
```
## Problem 3 (c)
```{r}
sample = rnorm(40, 132, 9.8)
quantile(sample, 0.9)
```

# Problem 4
## Problem 4 (a)
```{r}
## sample mean = 75, sd = 8, sample size = 30
error = qnorm(0.975) * 8 / sqrt(30)
lower = 75 - error
upper = 75 + error
c(lower, upper)
```
## Problem 4 (b)
### We are 95% confident that the population parameter is between `r lower` and `r upper`.

## Problem 4 (c)
### Yes, we don't need to do extra calculation to reject H0, because the 95% confidence interval is between `r lower` and `r upper`, which does not contain "70". Therefore, the null hypothesis µ = µ0 is rejected.




